\documentclass[twoside,10pt]{article}
\usepackage[latin1]{inputenc}
\usepackage[english,french]{babel}
\usepackage{multicol}
\usepackage{a4wide}
%\usepackage{a5}
%\usepackage{graphics}
\usepackage{fancyhdr}
\usepackage{verbatim}
%\usepackage{hyperref}
\usepackage{lettrine}
%\usepackage{times}
%\usepackage[Glenn]{fncychap}
\usepackage{color} 
%\usepackage{draftcopy}
%\usepackage{SFHeaders}

\bibliographystyle{amsplain}

%\usepackage{hieroglf} % hieroglyphes

%dvips  -T 14.85cm,21cm -o amap_srs.ps amap_srs.dvi; psbook amap_srs.ps tmp.ps ;  psnup -2 -pa4 -Pa5 tmp.ps tmpa4.ps; pstops '2:0U(21cm,29.7cm),1' tmpa4.ps amap_srs.ps
%psselect -p1 amap_srs.ps |lpr
% on prends la feuille, on la retourne et rement ds le bac intermediaire
%psselect -p2 amap_srs.ps |lpr

%\usepackage{geometry}

%\geometry{verbose,paperwidth=148.5mm,paperheight=210mm,
%  tmargin=15mm,bmargin=15mm ,lmargin=25mm,rmargin=20mm}
\usepackage{graphicx} 
\DeclareGraphicsExtensions{.eps} 

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\cfoot{$\thepage$}

\title{\bf Amap Software Requirements Specification\\ (SRS)}
%\date{}
\author{Antoine Lucas\thanks{e-mail: antoinelucas@gmail.com}\\[0.2cm]
\normalsize Brest
}

\newcounter{numeroreq}

	
\newcommand{\req}[1]{\stepcounter{numeroreq} \small{ \em \noindent [BEGIN REQUIREMENT AMAP\_SRS\_\arabic{numeroreq}] }\\ \noindent \rm \normalsize #1 \\ \small{ \em \noindent [END REQUIREMENT] \\ } }

\begin{document}


\maketitle

\sloppy


%% \begin{table}[htb]
%% \centering
%% \begin{tabular}{cc}
%% \hline
%% \bf Name & \bf e-mail \\
%% \hline
%% \hline
%% Antoine Lucas & antoinelucas@gmail.com\\
%% \hline
%% \end{tabular}
%% \caption{Authors}
%% \end{table}

\begin{table}[htb]
\centering
\begin{tabular}{ccc}
\hline
\bf Version & \bf date & \bf Update \\
\hline
\hline
0.1 & 30/09/2007  & Initial revision\\
\hline
\end{tabular}
\caption{Version history}
\end{table}

\begin{multicols}{2}

\section{Introduction}


%\subsection{Purpose}

Aim of amap package is to propose to end users (statistician and bioolgists)
powerfull  analysis tools. Statisticians requires many options and new 
algorithms as described in  \cite{caussinu+ruiz2} whereas biologists
needs very optimised standard algorithms. This package will be based on R 
language.



\section{Overall description}


Amap package will be a standard R package, using convention 
described in \cite{R:writtingRExt}.

It will provides
\begin{itemize}
\item implementation of new algorithms of robust pca
  described in \cite{caussinu+ruiz2},
\item implementation of new algorithm of optimal partition described in
\cite{mpetijean},
\item  a k-means algorithm based on a rank-metric,
\item  a hierarchical clustering optimised for multi-processor 
servers, with the minimum memory allocation.
\item the possibility to use rank based metrics with hierarchical clustering 
\end{itemize}



\section{Requirements}


\subsection{Scope}
\req{Amap package must implement algorithms described in \cite{caussinu+ruiz2}.}

\req{Amap package must implement algorithms described in \cite{mpetitjean}.}


\req{Amap package must implement a k-means algorithm based on a rank-metric.}

\req{Amap package must implement a rank based metrics with hierarchical clustering.}



\subsection{Performances}
\req{All algorithm must be coded in fortran, C or C++; R code will
be limited to data manipulation}


\req{Hierarchical clustering must compute a set of 15000 individuals with 200
variables on a dual Xeon 3.2~Ghz in less than 
half an hour with less than 1 Go memory used.}


\section{Methods, tools and techniques}

\req{Amap package will be a standard R package, using convention 
described in \cite{R:writtingRExt}. All function must have a user
manual}


\section{Qualification}

Amap package will provides a set of unitary tests, in order to check both 
exactitude of algorithms, and non regression.\\

\req{All algorithms will be ``proven'' by comparison to another implementation
with some references data tests}

\req{All functions have an example detailed in documentation, that command R CMD check is able to run without error. Output of theses examples will be archived
in order to check non regression.}

\req{An R script will test all functions with the combinaison of 
all parameters. Output of this script will be archived in order to check 
non regression.}


\bibliography{amap}

\end{multicols}

\end{document}
